Some examples in extended logic counting classes

### 2016-10-26 QSO/cap-comp.tex
26 oct

	As a first approach, we will use a 9-tuple $\bar{a} = (a_1,\ldots,a_9)$ to represent $s$. That is, $(a_1,a_2) = (1,A)$ represent the position of the head in the input tape, $a_3 = 2$ represents the position of the head in the working tape, $a_4 = C$ (1100b in base 16) represents the content of the working tape, and $(a_5,\ldots,a_9) = (0,0,1,0,0)$ represents the current state. Then $\bar{a} = (1,A,2,C,0,0,1,0,0)$ will represent $s$. It is not possible \martin{no se si ser\'a cierto esto} to find the $i$-th bit of an element $x$, or much less switch the $i$-th bit of an element, solely with $\fo$. So consider the following procedure.

	\begin{algorithm}
	\caption{If the $i$-th bit in $x$ is 1 replace it by 0}
	\begin{algorithmic}
		\State $b \gets bit(x,i)$
		\State $\textbf{assert } b = 1$
		\State $y = pow2(i)$
		\State $z = substract(x,y)$
		\State \Return $z$.
	\end{algorithmic}
	\end{algorithm}	
	And the details for $bit$, $pow2$ and $substract$ are left for the reader as an exercise.

	Note that there is an upper bound of $(n^2+2)\cdot (c\log(n)+2)\cdot 3^{c\log n} \cdot \ell$ distinct configurations in $M(w)$. Given a configuration $s\in M(w)$, we construct a tuple $\bar{a} = (a_0,\ldots,a_{k-1})$ that represents $s$.
	\begin{itemize}
	\item $(a_0,a_1,a_2)$ represent the position of the head in the reading tape. If $a_0 = 1$, then the head is in position $a_1a_2$ (the $a_1a_2$-th character in the input). If $a_1 = 2$, then $a_2 = 1$ represents that the head is at the beginning of the tape (position 0), and if $a_2 = 2$, then the head is at position $n+1$.
	\item $a_3$ represents the position of the head in the working tape.
	\item $(a_4,\ldots,a_{3+2c})$ represents the string that is in the working tape. Specifically, let $h$ be the value of $a_{3+2c}a_{2+2c}\cdots a_{5}a_{4}$ in base $n$. Then the string in the working tape is $h$ in base 3, where 2 is interpreted as $\texttt{B}$.
	\item $(a_{4+2c},\ldots,a_{3+2c+\ell})$ represents the current state $q_i$. Every value in the tuple is $1$ except the element $a_{3+2c+i}$ which is 2.	
	\end{itemize}

	Now we describe the formulas.
	\begin{align*}
	\varphi_I(\bar{x}) &= \varphi_v(\bar{x}) \wedge \exists u(\varphi_1(u) \wedge \varphi_{succ}(u,x_{3+e+2c})), \\
	\varphi_F(\bar{x}) &= \varphi_v(\bar{x}) \wedge \exists u(\varphi_1(u) \wedge \varphi_{succ}(u,x_{2+e+2c+\ell})),
	\end{align*}
	where $\varphi_v(\bar{x})$ describes that $\bar{x}$ is a valid configuration of $M(w)$ and $\varphi_1(x)$ describes that $x$ is the first element of $A$.
	\begin{align*}
	\varphi_v^1(\bar{x}) &= \exists u(\varphi_1(u) \wedge (x_1 = u \vee \varphi_{succ}(u,x_1)) \wedge \varphi_{succ}(u,x_1) \to (x_2 = u \vee \varphi_{succ}(u,x_2))), \\
	\varphi_v^4(\bar{x}) &= \exists u(\varphi_1(u) \wedge \bigvee_{i = 1}^{\ell}(\varphi_{succ}(u,x_{2+e+2c+i})  \wedge \bigwedge\limits_{\substack{i = 1\\ j \neq i}}^{\ell} x_{2+e+2c+j} = u)).
	\end{align*}
\end{proof}

>>>>

	As a first approach, we will use a 9-tuple $\bar{a} = (a_1,\ldots,a_9)$ to represent $s$. That is, $(a_1,a_2) = (1,A)$ represent the position of the head in the input tape, $a_3 = 2$ represents the position of the head in the working tape, $a_4 = C$ (1100b in base 16) represents the content of the working tape, and $(a_5,\ldots,a_9) = (0,0,1,0,0)$ represents the current state. Then $\bar{a} = (1,A,2,C,0,0,1,0,0)$ will represent $s$.

	The problem that arises from this representation, is that to describe a transition in $M$ we need to read an arbitrary character in the working tape, and therefore we have to obtain the $a_3$-th bit in $a_4$. Furthermore, to get the following configuration, we need compute $a_4$ with the $a_3$-th bit flipped. This is generally not possible to describe with an $FO$ formula. Consider the following procedure that receives $x = a_4$ and $i = a_3$.

	\begin{algorithm} \label{switch1to0}
	\caption{If the $i$-th bit in $x$ is 1 replace it by 0 and return the result}
	\begin{algorithmic}
		\State $u \gets x,\; j \gets i$ \Comment{Get the $i$-th bit on $x$ and store it in $u$}
		\While{$j > 0$}
		\State $v \gets 0$
		\While{$u > 1$}
		\State $u \gets u-2,\; v \gets v+1$
		\EndWhile
		\State $u\gets v,\; j \gets j-1$
		\EndWhile
		\While{$u > 1$}
		\State $u \gets u-2$
		\EndWhile
		\State $\textbf{assert } u = 1$ \Comment{If $u \neq 1$ simply stop}	
		\State $y \gets 1$ \Comment{Compute $2^i$ and store it in $y$}
		\While{$i > 0$}
		\State $z \gets 0$
		\While{$y > 0$}
		\State $z \gets z+2,\; y \gets y-1$
		\EndWhile
		\State $i \gets i-1,\; y \gets z$
		\EndWhile
		\While{$y > 0$} \Comment{Substract $y$ from $x$}
		\State $x \gets x-1,\; y \gets y-1$
		\EndWhile
		\State \Return $x$.
	\end{algorithmic}
	\end{algorithm}	
	Each of the instructions can be expressed with $\fo$, so our strategy is to use the $\pth$ operator to simulate the algorithm and then we can describe a transition using the processed value of $a_4$. Note that we need to describe three more procedures to simulate the transitions for $0\to 0$, $0 \to 1$ and $1\to 1$.

	We will now describe how to simulate both the procedure and the transition. A procedure tuple $\bar{p} = (a_1,\ldots,a_{3+c+\ell},b_1,b_2,c_1,c_2,c_3,d_1,\ldots,d_{5c+2})$ represents the current configuration of $M(w)$ in $a_1,\ldots,a_{2+c+\ell}$, the values that will be read and written in the working tape in $b_1,b_2$, the instruction pointer in $c_1,c_2,c_3$ and the values stored in memory in $d_1,\ldots,d_{10c+2}$. In detail:
	\begin{enumerate}
		\item $a_1,a_2$ and $a_3$ represent the position of the head in the input tape and the working tape, respectively, $a_4,\ldots,a_{3+c}$ represent the content of the working tape and $a_{4+c},\ldots,a_{3+c+\ell}$ represent the current state in the current configuration that is being processed.
		\item $b_1$ and $b_2$ are equal to the value that is being read in the working tape and the value that will be written in the working tape respectively.
		\item $c_1,c_2,c_2$ represent the instruction pointer in the procedure. Only 8 different instructions are needed in the simulation.
		\item Each value in memory of $x,y,z,u,v$ need $c$ elements to represent them and $i,j$ need only one. We map $(d_1\ldots,d_{c}) \to x$, $(d_{c+1}\ldots,d_{2c}) \to y$,
		$(d_{2c+1}\ldots,d_{3c}) \to z$, $(d_{3c+1}\ldots,d_{4c}) \to u$,
		$(d_{4c+1}\ldots,d_{5c}) \to v$, $d_{5c+1} \to i$ and $d_{5c+2}\to j$.
	\end{enumerate}
	For each transition $\delta \subseteq Q \times \{0,1\} \times \{0,1\} \times Q \times \{-1,=,+1\} \times \{0,1\} \times \{-1,=,+1\}$ we define a formula $\varphi_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v})$, where $\bar{x} = (x_1,\ldots,x_{3+c+\ell})$, $\bar{s} = (s_1,s_2)$, $\bar{w} = (w_1,w_2,w_3)$, $\bar{u} = (u_1,\ldots,u_{5c+2})$, $\bar{y} = (y_1,\ldots,y_{3+c+\ell})$, $\bar{t} = (t_1,t_2)$, $\bar{z} = (z_1,z_2,z_3)$ and $\bar{v} = (v_1,\ldots,v_{5c+2})$ that describes the procedure to compute the values in the configuration and the transition itself. We will describe the formula part by part. Suppose $\delta = (q_i,a,1,q_j,op_1,0,op_2)$, so we have to simulate Algorithm \ref{switch1to0}.

	We start from instruction 0, which means that the procedure has not started yet and every value in the tuple is 0 except for the configuration values. It also initializes all the values in the tuple to 0 except for $x,u,i,j$.
	\begin{multline*}
	\varphi^{0,1}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{0,0}(s_1,s_2)\wedge\varphi^b_0(\bar{w}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_1(\bar{z})\, \wedge \\ 
	\bigwedge_{i = 1}^c v_i = x_{3+i} \wedge \bigwedge_{i = c+1}^{2c} \varphi_0(v_i) \wedge \bigwedge_{i = 2c+1}^{3c} \varphi_0(v_i) \wedge \bigwedge_{i = 1}^c v_{3c+i} = x_{3+i} \wedge \bigwedge_{i = 4c+1}^{5c} \varphi_0(v_i) \wedge v_{5c+1} = x_3 \wedge v_{5c+2} = x_3.
	\end{multline*}
	Instruction 1 which checks whether the value of $j$ ($d_{5c+2}$ in the tuple) is more than 0 or not, and then proceeds to instruction 2 or 3 on each case.
	\begin{multline*}
	\varphi^{1,2}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = 
	\varphi_{1,0}(s_1,s_2) \wedge \varphi^b_1(\bar{w}) \wedge \neg \varphi_0(u_{5c+2}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_2(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i, \\
	\varphi^{1,3}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = 
	\varphi_{1,0}(s_1,s_2) \wedge \varphi^b_1(\bar{w}) \wedge \varphi_0(u_{5c+2}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_3(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i.
	\end{multline*}
	Instruction 2 checks the value of $u$ ($d_{3c+1},\ldots,d_{4c}$ in the tuple). If it is $> 1$ then it substracts 2 from $u$ and adds 1 to $v$ ($d_{4c+1},\ldots,d_{5c}$ in the tuple), then repeats instruction 2. If it is equal to 0 or 1, then moves the value of $v$ to $u$, substracts 1 from $j$ and goes back to instruction 1.
	\begin{multline*}
	\varphi^{2,2}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = 
	\varphi_{1,0}(s_1,s_2) \wedge \varphi^b_2(\bar{w}) \wedge \neg \varphi^m_0(u_{3c+1},\ldots,u_{4c}) \wedge \neg \varphi^m_1(u_{3c+1},\ldots,u_{4c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_2(\bar{z})\, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\bigwedge_{i = c+1}^{2c} u_i = v_i \wedge
	\bigwedge_{i = 2c+1}^{3c} u_i = v_i \wedge
	\varphi^m_{-2}(u_{3c+1},\ldots,u_{4c},v_{3c+1},\ldots,v_{4c})\, \wedge \\
	\varphi^m_{+1}(u_{4c+1},\ldots,u_{5c},v_{4c+1},\ldots,v_{5c}) \wedge u_{5c+1} = v_{5c+1} \wedge u_{5c+2} = v_{5c+2}. \\
	\varphi^{2,1}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_2(\bar{w}) \wedge ( \varphi^m_0(u_{3c+1},\ldots,u_{4c}) \vee \varphi^m_1(u_{3c+1},\ldots,u_{4c})) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_1(\bar{z})\, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\bigwedge_{i = c+1}^{2c} u_i = v_i \wedge
	\bigwedge_{i = 2c+1}^{3c} u_i = v_i \wedge
	\bigwedge_{i = 3c+1}^{4c} u_{c+i} = v_i \wedge
	\varphi^m_0(v_{4c+1},\ldots,v_{5c}) \wedge
	u_{5c+1} = v_{5c+1} \wedge \varphi_{-1}(u_{5c+2},v_{5c+2}).	
	\end{multline*}
	Instruction 3 calculates the value of $u \mod 2$, that is, it repeats instruction 3 until the value of $u$ is equal to 0 or 1. On each iteration, it substracts 2 from $u$. Moreover, if the value of $u$ at the end of the iterations is not 1 then there is no step defined.
	\begin{multline*}
	\varphi^{3,3}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_3(\bar{w}) \wedge \neg \varphi^m_0(u_{3c+1},\ldots,u_{4c}) \wedge \neg \varphi^m_1(u_{3c+1},\ldots,u_{4c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_3(\bar{z})\, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\bigwedge_{i = c+1}^{2c} u_i = v_i \wedge
	\bigwedge_{i = 2c+1}^{3c} u_i = v_i \wedge
	\varphi^m_{-2}(u_{3c+1},\ldots,u_{4c},v_{3c+1},\ldots,v_{4c}) \wedge
	\bigwedge_{i = 4c+1}^{5c} u_i = v_i \wedge
	u_{5c+1} = v_{5c+1} \wedge u_{5c+2} = v_{5c+2}, \\
	\varphi^{3,3}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = 
	\varphi_{1,0}(s_1,s_2) \wedge \varphi^b_3(\bar{w}) \wedge \varphi^m_1(u_{3c+1},\ldots,u_{4c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_4(\bar{z})\, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\varphi^m_1(v_{c+1},\ldots,v_{2c}) \wedge
	\bigwedge_{i = 2c+1}^{3c} u_i = v_i \wedge
	\bigwedge_{i = 3c+1}^{4c} u_i = v_i \wedge
	\bigwedge_{i = 4c+1}^{5c} u_i = v_i \wedge
	u_{5c+1} = v_{5c+1} \wedge u_{5c+2} = v_{5c+2}
	\end{multline*}
	Instruction 4 checks the value of $i$ ($d_{5c+1}$ in the tuple.) If it is not 0 then goes to instruction 5 and if is 0 then goes to instruction 6. Moreover it initializes the value of $z$ ($d_{2c+1},\ldots,d_{3c}$ in the tuple) to 0 (which was 0 all along.)
	\begin{multline*}
	\varphi^{4,5}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_4(\bar{w}) \wedge \neg \varphi_0(u_{5c+1}) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_5(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i, \\
	\varphi^{4,6}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_4(\bar{w}) \wedge \varphi_0(u_{5c+1}) \wedge \varphi_{1,0}(t_1,t_2) \wedge 	\varphi^b_6(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i.
	\end{multline*}
	Instruction 5 checks the value of $y$ ($d_{c+1},\ldots,d_{2c}$ in the tuple.) If it is more than 0 then it adds 2 to $z$ and substracts 1 from $y$, then repeats instruction 2. If it is not, then copies the value of $z$ to $y$ and subtracts 1 from $i$ and returns to instruction 4.
	\begin{multline*}
	\varphi^{5,5}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_5(\bar{w}) \wedge \neg \varphi^m_0(u_{c+1},\ldots,u_{2c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_5(\bar{z}) \, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\varphi^m_{-1}(u_{c+1},\ldots,u_{2c},v_{c+1},\ldots,v_{2c}) \wedge
	\varphi^m_{+2}(u_{2c+1},\ldots,u_{3c},v_{2c+1},\ldots,v_{3c})\, \wedge \\
	\bigwedge_{i = 3c+1}^{4c} u_i = v_i \wedge
	\bigwedge_{i = 4c+1}^{5c} u_i = v_i \wedge
	u_{5c+1} = v_{5c+1} \wedge u_{5c+2} = v_{5c+2}, \\
	\varphi^{5,4}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_5(\bar{w}) \wedge \varphi^m_0(u_{c+1},\ldots,u_{2c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_4(\bar{z}) \, \wedge \\
	\bigwedge_{i = 1}^c u_i = v_i \wedge
	\bigwedge_{i = c+1}^{2c} u_{c+i} = v_i \wedge
	\varphi^m_0(v_{2c+1},\ldots,v_{3c}) \wedge
	\bigwedge_{i = 3c+1}^{4c} u_i = v_i \wedge
	\bigwedge_{i = 4c+1}^{5c} u_i = v_i \wedge
	\varphi_{-1}(u_{5c+1},v_{5c+1}) \wedge u_{5c+2} = v_{5c+2}
	\end{multline*}
	Instruction 6 checks the value of $y$. If it is more than 0, then subtracts 1 from $x$ and $y$ and repeats instruction 6. If it is not, then goes to instruction 7.
	\begin{multline*}
	\varphi^{6,6}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_6(\bar{w}) \wedge \neg \varphi^m_0(u_{c+1},\ldots,u_{2c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_6(\bar{z}) \, \wedge \\
	\varphi^m_{-1}(u_1,\ldots,u_c,v_i,\ldots,v_c) \wedge \varphi^m_{-1}(u_{c+1},\ldots,u_{2c},v_{c+1},\ldots,v_{2c}) \wedge \bigwedge_{i = 3c+1}^{5c+2} u_i = v_i]\,\vee \\
	\varphi^{6,7}_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = \varphi_{1,0}(s_1,s_2) \wedge \varphi^b_6(\bar{w}) \wedge \varphi^m_0(u_{c+1},\ldots,u_{2c}) \wedge \varphi_{1,0}(t_1,t_2) \wedge \varphi^b_7(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i.
	\end{multline*}
	Instruction 7 stores the value of $x$ after the corresponding bit has been switched. Then we can define $\varphi_{\delta}$ which also simulates the actual transition. If $u$ equals 1, then copy what is stored in $x$ to $a_4,\ldots,a_{3+c}$, go from state $q_i$ to state $q_j$, and move the heads to their corresponding positions.
	\begin{multline*}
	\varphi_{\delta}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) = 	[\bigwedge_{i = 1}^{3+c+\ell} x_i = y_i \wedge (\varphi^{0,1}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{1,2}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v})\, \vee \\ \varphi^{1,3}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{2,2}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{2,1}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{3,3}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \\ \varphi^{3,4}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{4,5}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{4,6}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{5,5}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \\ \varphi^{5,6}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{6,6}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}) \vee \varphi^{6,7}(\bar{x},\bar{s},\bar{w},\bar{u},\bar{y},\bar{t},\bar{z},\bar{v}))] \, \vee \\
	[\varphi_{1,0}(s_1,s_2) \wedge \varphi^b_7(\bar{w}) \wedge \varphi^m_1(u_{3c+1},\ldots,u_{4c}) \wedge \varphi_{0,0}(t_1,t_2) \wedge \varphi^b_0(\bar{z}) \wedge \bigwedge_{i = 1}^{5c+2} u_i = v_i \,\wedge \\
	\varphi^2_{op_1}(x_1,x_2,y_1,y_2) \wedge \varphi_{op_2}(x_3,y_3) \wedge \bigwedge_{i = 1}^c u_i = x_{3+i} \wedge \varphi^q_i(x_{4+c},\ldots,x_{3+c+\ell}) \wedge \varphi^q_j(y_{4+c},\ldots,y_{3+c+\ell})].
	\end{multline*}
	Note that we also need to specify that the program we are following is Algorithm \ref{switch1to0} so we store $1,0$ in $b_1,b_2$ all along the procedure. We now describe the three other algorithms that compute the switches from $0\to 0$, $0\to 1$ and $1\to 1$.
\end{proof}
